|

### 2022-07-04 manuscript.Rmd
tidy up references

bibliography: JDSbib.bib
output:
  rticles::jds_article: default
  bookdown::pdf_book:
    base_format: rticles::jds_article # for using bookdown features like \@ref()
---

@@

According to LinkedIn's 2017 U.S. Emerging Jobs Report, machine learning engineers and data scientists rank among the top emerging jobs.
With the urgent need for training a higher number of skilled data scientists, many institutes of higher education are developing their own data science curricula and a consensus on what should be included in such curricula has not yet been reached. 
In the latest version of *Computing Competencies for Undergraduate Data Science Curricula* by ACM Data Science Task Force, accessibility is a recommended content for the data science curricula \cite{danyluk2021computing}.

>>>>

bibliography: "bib/references.bib"
output:
  rticles::jds_article: default
  bookdown::pdf_book:
    base_format: rticles::jds_article # for using bookdown features like \@ref()
---

@@

According to LinkedIn's 2017 U.S. Emerging Jobs Report, machine learning engineers and data scientists rank among the top emerging jobs.
With the urgent need for training a higher number of skilled data scientists, many institutes of higher education are developing their own data science curricula and a consensus on what should be included in such curricula has not yet been reached. 
In the latest version of *Computing Competencies for Undergraduate Data Science Curricula* by ACM Data Science Task Force, accessibility is a recommended content for the data science curricula @danyluk2021computing.
